\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry} % Reduced margin for one page
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% Formatting
\pagestyle{empty}
\raggedright
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.3em} % Reduced skip

% Section Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt} % Compact spacing

% Custom Itemize
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt}

\begin{document}

%======================
% Header
%======================
\begin{center}
    {\Huge \textbf{Ronnie A Jeffrey}} \\[0.3em]
    \href{mailto:ronnieallen2005@gmail.com}{ronnieallen2005@gmail.com} \quad | \quad +91 99528 60468 \\[0.2em]
    \href{https://www.linkedin.com/in/ronnie-a-jeffrey/}{linkedin.com/in/ronnie-a-jeffrey} \quad | \quad 
    \href{https://github.com/ronnie-allen}{github.com/ronnie-allen} \quad | \quad 
    \href{https://ronnie-a-jeffrey.tech}{ronnie-a-jeffrey.tech}
\end{center}

%======================
\section{Education}
%======================
\textbf{Karunya Institute of Technology} \hfill Coimbatore, India \\
B.Tech in Artificial Intelligence and Data Science \hfill May 2027

%======================
\section{Experience}
%======================
\textbf{CoreInsightsAI} \hfill Bangalore, India \\
\textit{AI and Software Developer} \hfill Jun 2025 – Present
\begin{itemize}
  \item Developed scalable applications in Next.js with integrated LLM-based automation.
  \item Worked on full-stack solutions, AI-driven features, and light DevOps workflows.
\end{itemize}

\textbf{Karunya Innovative Design Studio (KIDS)} \hfill Coimbatore, India \\
\textit{Full Stack and Mobile App Trainee} \hfill Aug 2024 – Mar 2025
\begin{itemize}
  \item Built frontend interfaces using React.js and integrated APIs.
  \item Participated in backend development using Node.js for university platforms.
\end{itemize}

\textbf{Nandha Infotech} \hfill Coimbatore, India \\
\textit{Mobile App Developer Intern} \hfill Jun 2024 – Jul 2024
\begin{itemize}
  \item Built Flutter-based mobile UIs for agriculture-focused applications.
  \item Integrated APIs and improved UX in real-time delivery apps.
\end{itemize}

%======================
\section{Skills}
%======================
\textbf{Frontend:} HTML, CSS, JavaScript, TypeScript, React, Tailwind, Bootstrap, Gradio \\
\textbf{Backend:} Node.js, Python, FastAPI, MongoDB, Firebase \\
\textbf{Mobile:} Flutter, Dart \\
\textbf{AI/ML:} TensorFlow, Sci-Kit, Java, Ollama, PydanticAI, Langchain, Langgraph, Langsmith, CrewAI \\
\textbf{Tools:} Git, VS Code, Postman, Figma, Docker, Linux, HuggingFace, GitHub, N8N

%======================
\section{Projects}
%======================
\textbf{MindKraft '25 - An Event Site} \\
Full-featured event site with auth, payment, and user dashboard. \\
\textit{Tech Stack: React, Node.js, Payment API}

\textbf{Music Genre Classification with CNN} \\
Audio classifier using CNN and Librosa features to predict music genres. \\
\textit{Tech Stack: Python, TensorFlow, Keras, Streamlit}

\textbf{Water Potability Prediction} \\
ML model deployed via Django comparing XGBoost, LSTM, and Random Forest. \\
\textit{Tech Stack: React.js, Django, ShadCN UI}

\textbf{Patient Monitoring System} \\
AI-driven platform for tracking patients by analyzing lab reports. \\
\textit{Tech Stack: AI, Web Technologies}

\textbf{CropAI - Crop Recommendation \& Yield Prediction} \\
ML system for crop planning and yield estimation using Random Forest. \\
\textit{Tech Stack: Django, React.js, Scikit-learn}

\textbf{UNISCAN - Smart Attendance System} \\
Face recognition attendance system with barcode verification for IoT. \\
\textit{Tech Stack: Computer Vision, IoT, Excel Integration}

\textbf{BlogRelay - Blog Writer Agent} \\
Agentic workflow to turn topics into polished blogs using LLMs. \\
\textit{Tech Stack: FastAPI, Mistral AI, CrewAI, Gmail API}

%======================
\section{Certifications}
%======================
\textbf{Google CyberSecurity Specialization} \hfill Jul 2024 \\
\textbf{Data Analytics Internship} – YBI Foundation \hfill Sep 2024 \\
\textbf{CSS Skill Test} – HackerRank \hfill Sep 2024 \\
\textbf{Java Programming Fundamentals} – Infosys \hfill Sep 2024

\end{document}
